Using tours to visually investigate properties of new projection pursuit indexes with application to problems in physics

### 2019-06-18 scagnostics.Rmd
Removing obsolete comment.
textcolors to textcolor

\textcolors{red}{To use the existing index functions on real-world datasets we recommend to either use the tourr package directly, or if interaction is required to call the guided tour via the graphical interface available in the galahr [XXX Ref] package. Both packages contain examples to show how the guided tour can be used with different index functions.}

@@

\textcolor{red}{Mention spinebil and galahr packages, some statement about big data (addressing the AE question). Mention d>2 as subject of future work.}

>>>>

\textcolor{red}{To use the existing index functions on real-world datasets we recommend to either use the tourr package directly, or if interaction is required to call the guided tour via the graphical interface available in the galahr [XXX Ref] package. Both packages contain examples to show how the guided tour can be used with different index functions.}

@@
